An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-10-06 paper.tex
Tweak authors/affiliations
Fix affiliation
Discuss Internet-drafts

\title{An Empirical Analysis of the Internet Engineering Task Force 
       with Computational Methods}
\author[1]{Mladen Karan}
\author[1]{Prashant Khare}
\author[2]{Ravi Shekhar}
\author[1]{Matthew Russell Barnes}
\author[1]{Waleed Iqbal}
\author[3]{Junaid Qadir}
\author[4]{Stephen McQuistin}
\author[1]{Richard G. Clegg}
\author[1]{Patrick Healey}
\author[5]{Matthew Purver}
\author[1]{Ignacio Castro}
\author[6]{Gareth Tyson}
\author[7]{Colin Perkins}

\affil[1]{Queen Mary University of London}
\affil[2]{University of Essex}
\affil[3]{Information Technology University}
\affil[4]{University of St Andrews}
\affil[5]{Jozef Stefan Institute}
\affil[6]{Hong Kong University of Science \& Technology}
\affil[7]{University of Glasgow}

@@

\todo{Plot RFC publication count as a cumulative distribution}

In addition to the published RFCs, we track work-in-progress documents,
known as Internet-drafts, that are intended for eventual publication as
RFCs.
\todo{Add internet-draft counts over time as mentioned in Section \ref{sec:org-dyn:participants}}

@@

@@

%--------------------------------------------------------------------------------------------------
\subsection{What Makes a Successful Author?}
% ICWSM 2022 paper Section 4

@@

%--------------------------------------------------------------------------------------------------
\subsection{What Makes a Successful Document?}

>>>>

\title{An Empirical Analysis of the Internet Engineering Task Force with Computational Methods}

\author[1]{Mladen Karan}
\author[1]{Prashant Khare}
\author[2]{Ravi Shekhar}
\author[1]{Matthew Russell Barnes}
\author[1]{Waleed Iqbal}
\author[3]{Junaid Qadir}
\author[4]{Stephen McQuistin}
\author[1]{Richard G. Clegg}
\author[1]{Patrick Healey}
\author[5]{Matthew Purver}
\author[1]{Ignacio Castro}
\author[6]{Gareth Tyson}
\author[7]{Colin Perkins}

\affil[1]{Queen Mary University of London}
\affil[2]{University of Essex}
\affil[3]{Qatar University}
\affil[4]{University of St Andrews}
\affil[5]{Jo\v{z}ef Stefan Institute}
\affil[6]{Hong Kong University of Science \& Technology}
\affil[7]{University of Glasgow}

\date{7 October 2024}

@@

@@

%..................................................................................................
\pb{Internet-Drafts:}
Figure \ref{fig:drafts-by-date} shows the number of working documents,
known as Internet-drafts, that were active in the IETF over time. An
Internet-draft is a limited lifetime working document that expires after
six months, when replaced by a new version, or then published as an RFC.

We observe that the number of active drafts correlates more strongly with
the number of active working groups (Figure \ref{fig:pub_wgs_yearly}) than
with RFC publication (Figure \ref{fig:rfcs_by_area}).  This is largely to
be expected: an Internet-Draft is a work-in-progress document that is
proposed for adoption by, and discussion in, an IETF working group prior to
eventual publication as an RFC.  Competing proposals are often submitted as
drafts, to allow a working group to review them and make a decision how to
proceed, and hence not all drafts become RFCs. As we discuss in
\S\ref{sec:success-factors:documents}, draft adoption is a significant
milestone.

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures/drafts-by-date.pdf}
  \caption{
    Number of active drafts over time. Internet-Drafts, working documents
    of the IETF for work that was intended for eventual publication as an
    RFC, were introduction at the 13th IETF meeting in 1989.
  }
  \label{fig:drafts-by-date}
\end{figure}

@@

%--------------------------------------------------------------------------------------------------
\subsection{What Makes a Successful Author?}
\label{sec:success-factors:authors}

% ICWSM 2022 paper Section 4

@@

%--------------------------------------------------------------------------------------------------
\subsection{What Makes a Successful Document?}
\label{sec:success-factors:documents}
